%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Lucy L. W. Owen} % Your name
\address{8 Sachem Circle Unit 4, \\ West Lebanon, NH 03784} % Your address
\address{Lucy.W.Owen.GR@dartmouth.edu \\ (859) 576-4570 \\ lucywowen.github.io} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Dartmouth College} \hfill {\em 2016 - present} 
\\ Ph.D. student: Psychological and Brain Sciences

{\bf Columbia University, Teachers College} \hfill {\em 2013 - 2014} 
\\ Master of Science: Neuroscience and Education
\\ Thesis: The Role of Dopamine in Memory
\\ Psi Chi, Psychology Honors Organization

{\bf Davidson College} \hfill {\em 2006 - 2010} 
\\ Bachelor of Arts 
\\ Major in Studio Art, Minor in Chemistry, Pre-Medicine Concentration

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages &  Python, JavaScript, MATLAB \\
Software \& Tools & Numpy, PANDAS Scikit-learn, Bash, Git,  Docker \\
Neuropsychological Assessment & MOCA, NART,Trails A \& B, Category Fluency, Digit Span \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

%------------------------------------------------

\begin{rSubsection}{Ph.D. student, Dartmouth College}{2016 - present}{PI: Dr. Jeremy Manning}{}
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Lab manager, Columbia University}{2014 - 2016}{PI: Dr. Daphna Shohamy}{}
\end{rSubsection}


%------------------------------------------------

\begin{rSubsection}{Research assistant, Columbia University Teachers College}{2013 - 2015}{PI: Dr. Peter Gordon}{}
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Publications
%----------------------------------------------------------------------------------------

\begin{rSection}{Publications} \itemsep -2pt

\item \textbf{Owen, LLW}, Heusser AC, Manning, JR (2018, October) A Gaussian process model of human electrocorticographic data. \textit{bioRxiv}: 121020.


\item \textbf{Owen, LLW}, Manning, JR (2017, May) Towards human Super EEG.
\textit{bioRxiv}: 121020.

\item Heusser AC, Ziman K, \textbf{Owen, LLW}, Manning JR (2018) HyperTools: A Python toolbox for gaining geometric insights into high-dimensional data. \textit{Journal of Machine Learning Research}, 18(152): 1 - 6.


\end{rSection}


%----------------------------------------------------------------------------------------
%	Talks
%----------------------------------------------------------------------------------------

\begin{rSection}{Talks} \itemsep -2pt

\item \textbf{Owen LLW}, Heusser AC, Sperling M, Lega B, Worrell G, Gross R, Jobst B, Davis K, Zaghloul KA, Sheth S, Stein J, Das S, Gorniak R, Manning JR (2018, November) Fast timescale network dynamics underlying episodic encoding and retrieval. \textit{Society for Neuroscience annual meeting}, San Diego, CA.

\item \textbf{Owen LLW} (2018, October) Fast timescale network dynamics underlying episodic encoding and retrieval using SuperEEG. \textit{Dartmouth Hitchcock Medical Center}, Lebanon, NH.

\item \textbf{Owen LLW} (2018, October) Timecorr: Dynamic correlations and higher order correlations.
\textit{Contextual Dynamics Lab meeting}, Hanover, NH. 

\item \textbf{Owen LLW}, Goldstien A (2018, August) Ausio correlations with predicted ECoG activity. \textit{Methods in Neuroscience at Dartmouth}, Hanover, NH.

\item \textbf{Owen LLW} (2018, August) Introduction to Docker. \textit{Methods in Neuroscience at Dartmouth}, Hanover, NH. \href{https://www.youtube.com/watch?v=hUvYdXo5MfU}{Link to video}.

\item \textbf{Owen LLW} (2018, July) Data Blitz.
\textit{EPSCoR Womens' Conference}, Providence, RI. 

\item \textbf{Owen LLW} (2018, May) Pycharm: Debugging, and Docker Integration.
\textit{Contextual Dynamics Lab meeting}, Hanover, NH.

\item \textbf{Owen LLW} (2018, April) Specialist departmental presentation. \textit{Department of Psychological and Brain Sciences, Dartmouth College}, Hanover, NH.

\item \textbf{Owen LLW} (2018, April) Lecture: Memory. \textit{Psychology I, Dartmouth College}, Hanover, NH.

\item \textbf{Owen LLW} (2018, March) Lecture: Learning. \textit{Psychology I, Dartmouth College}, Hanover, NH.

\item \textbf{Owen LLW} (2018, March) Testing and Continuous Integration in Python.
\textit{Contextual Dynamics Lab meeting}, Hanover, NH.

\item \textbf{Owen LLW} (2017, October) Lecture: Memory. \textit{Psychology I, Dartmouth College}, Hanover, NH.

\item \textbf{Owen LLW} (2017, September) Lecture: Learning. \textit{Psychology I, Dartmouth College}, Hanover, NH.

\item \textbf{Owen LLW} (2018, September) SuperEEG updates.
\textit{Contextual Dynamics Lab meeting}, Hanover, NH.

\item \textbf{Owen LLW} (2017, June) Towards human SuperEEG. \textit{Dartmouth Hitchcock Medical Center}, Lebanon, NH.


\end{rSection}



%----------------------------------------------------------------------------------------
%	Poster Presentations
%----------------------------------------------------------------------------------------

\begin{rSection}{Poster Presentations} \itemsep -2pt

\item \textbf{Owen LLW} Manning JR (2017, November). A Gaussian process model of
human ECoG data. \textit{Society for Neuroscience annual meeting},
Washington, DC.

\item Heusser AC, Ziman K, \textbf{Owen LLW}, Manning JR (2017, November).
HyperTools: A python toolbox for gaining geometric insights into high-dimensional
data. \textit{Society for Neuroscience annual meeting}, Washington, DC.

\item \textbf{Owen LLW}, Manning JR (2017, May) Towards human Super EEG.
\textit{Context and Episodic Memory Symposium}, Philadelphia, PA.

\item Heusser AC, Ziman K, \textbf{Owen LLW}, Manning JR (2017, May) HyperTools: A Python
toolbox for visualizing and manipulating high-dimensional data. \textit{Context and Episodic Memory Symposium}, Philadelphia, PA.

\item \textbf{Owen LLW}, Manning JR (2017, April) Towards human Super EEG.  \textit{Graduate student poster session}, Dartmouth College, Hanover, NH.

\item \textbf{Owen LLW}, Sharp ME, & Shohamy D (2016, April) Acquisition and consolidation of motor sequence learning in Parkinson’s disease.  \textit{Cognitive Neuroscience
Society Meeting}, New York, NY.

\item Gordon P, Kim S, Paz ML, Reddick E, \textbf{Owen LLW} (2014, April) The neural basis of parallel individuation and numerical estimation.  \textit{Cognitive Neuroscience
Society Meeting}, Boston, MA.

\item  Kim S,  \textbf{Owen LLW}, Levinson H, Paz ML, Gordon P (2014, April) Functional links of neural correlates of word meaning: Behavioral and Neurophysiological Evidence. \textit{Cognitive Neuroscience Society Meeting}, Boston, MA.

\end{rSection}


%----------------------------------------------------------------------------------------
%	Service
%----------------------------------------------------------------------------------------


\begin{rSection}{Service}

%------------------------------------------------

\begin{rSubsection}{Graduate representative, cognitive area}{2018 - 2020}{Liaison between graduate students and faculty as well as host for prospective graduate students.}{}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{EPSCoR Women’s conference}{Summer, 2018}{Attendee.}{}
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	Teaching experience
%----------------------------------------------------------------------------------------


\begin{rSection}{Teaching experience}

%------------------------------------------------

\begin{rSubsection}{Teaching Assistant}{Spring, 2018}
{Dartmouth College, Psychology I  
 \\ Course taught by Drs. Thalia Wheatly and Brad Duchaine}{}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Teaching Assistant}{Fall, 2017}
{Dartmouth College, Psychology I  
 \\ Course taught by Drs. Thalia Wheatly and Brad Duchaine}{}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Teaching Assistant}{Summer, 2017}
{Dartmouth College, Experimental Psychology 
\\ Course taught by Dr. Jeremy Manning}{}
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Teaching Assistant}{Spring, 2014}
{Columbia University, Teachers College, Brain and Behavior II
\\ Course taught by Dr. Peter Gordon}{}
\end{rSubsection}

\end{rSection}


\end{document}

